---
title: "Statistical Inference Assignment"
---

#### ------------------------------------------------------------------------
#### Part 1: Simulation exercises
#### ------------------------------------------------------------------------

```{r, echo=FALSE}
x <- c("")
for (i in 1:1000){x[i]<- mean(rexp(40,.2))}
dens<- dnorm(as.numeric(x), mean=5, sd=5)
plot(x,dens, main = "X-Normal: Mean = (1/.2), SD= (1/.2)", xlab = "x", ylab = "Prob Density", las=3)

##drawing the theoretical center when mean is 1/.2 = 5
abline(v=5, col="green")

##drawing the calculated center of the distribution
cMean <- mean(as.numeric(x))
abline(v=cMean,col="red")

## calculate the variance of the distribution
cVar <-0;
for (i in 1:1000) 
    {    
     cVar <- cVar + (as.numeric(x[i])-5)^2
    }

cVar <- cVar/(1000-1)

## Setting up the variables

a<-0; l <- c(""); u <- c("")

## Calculating the percentage of the generated means that lie with the 95% conf interval

for (i in 1:1000)
  {
    l[i]<-as.numeric(x[i]) - 1.96*5/sqrt(40)
    u[i]<-as.numeric(x[i]) + 1.96*5/sqrt(40)
    if(l[i]<=5 && u[i]>=5)
      {
      a<-a+1
      }
  }

b<- (a/1000)*100
   
```

Q1. In the graph the green line is the theoretical mean at 5 and the red line is calculated mean at `r cMean`.
As you can see the calculated the theoretical mean is approx. identical.

Q2. The theoretical variance is (1/.2)^2 = 25. The calculated real variance is `r cVar`. The real variance is significantly lower than the theoretical variance.


```{r, echo=FALSE}
par(mfrow=c(1,2))
hist(as.numeric(x), breaks=40, main="Histogram of X ", xlab="X")
qqnorm(as.numeric(x))
qqline(as.numeric(x))
```


Q3. Looking at the histogram and the corresponding qqplot you can see that the distribution is approx. normal with slightly fat tails

Q4. The approx. coverage of the confidence interval is `r a` out of 1000 or `r b` %

