---
title: "Statistical Inference Assignment"
---

#### ---------------------------------------------------------------------------------
#### Part 2: Basic inferential data analysis
#### ---------------------------------------------------------------------------------

Basic boxplots to summarize the data visually

```{r, echo=FALSE}

## Loading the data
data(ToothGrowth)

## basic boxplots to summarize the data visually
par(mfrow=c(1,2))
boxplot(len ~ supp, data = ToothGrowth)
boxplot(len ~ dose, data = ToothGrowth)
```

Basic data summary

```{r, echo=FALSE}
## Basic data summary 
summary(ToothGrowth)
```

t confidence and p value results for supp categories on length

```{r, echo=FALSE}
## t confidence interval tests for supp with the assumption that variance is TRUE and FALSE
rbind(
t.test(len~supp, paired=FALSE, var.equal=TRUE, data=ToothGrowth)$conf,
t.test(len~supp, paired=FALSE, var.equal=FALSE, data=ToothGrowth)$conf
)

## p value Hypothesis  for the same data
rbind(
t.test(len~supp, paired=FALSE, var.equal=TRUE, data=ToothGrowth)$p.value,
t.test(len~supp, paired=FALSE, var.equal=FALSE, data=ToothGrowth)$p.value
)

```

t confidence and p value results for dosage on length

```{r, echo=FALSE}
## t confidence interval tests for dose with the assumption that variance is TRUE and FALSE
len12 <- subset(ToothGrowth, dose %in% c(1,2))
len51 <- subset(ToothGrowth, dose %in% c(.5,1))
len52 <- subset(ToothGrowth, dose %in% c(.5,2))

rbind(
t.test(len~dose, paired=FALSE, var.equal=TRUE, data=len12)$conf,
t.test(len~dose, paired=FALSE, var.equal=FALSE, data=len12)$conf,
t.test(len~dose, paired=FALSE, var.equal=TRUE, data=len51)$conf,
t.test(len~dose, paired=FALSE, var.equal=FALSE, data=len51)$conf,
t.test(len~dose, paired=FALSE, var.equal=TRUE, data=len52)$conf,
t.test(len~dose, paired=FALSE, var.equal=FALSE, data=len52)$conf
)

##p value Hypothesis  for the same data


rbind(
t.test(len~dose, paired=FALSE, var.equal=TRUE, data=len12)$p.value,
t.test(len~dose, paired=FALSE, var.equal=FALSE, data=len12)$p.value,
t.test(len~dose, paired=FALSE, var.equal=TRUE, data=len51)$p.value,
t.test(len~dose, paired=FALSE, var.equal=FALSE, data=len51)$p.value,
t.test(len~dose, paired=FALSE, var.equal=TRUE, data=len52)$p.value,
t.test(len~dose, paired=FALSE, var.equal=FALSE, data=len52)$p.value
)


```
###### Conclusion : Impact of supplements and dosage on Tooth Length

1) We can't statistically say that the supplementary types have any impact on the length. The reason is zero lies between the t confidence intervals. The p value of approx. 6 % plus is statistically significant and we can't reject the null hypothesis that there is no difference because of the supp

2) Changes in Dosage between .5 to 1, .5 to 2, and 1 to 2 all has an impact on overall length. the t confidence intervals do not have zeroes and the p values are all significantly below 5%

###### Assumption

The key assumption is that the samples are all from the same population. 
However the finding with this assumption as TRUE or FALSE does not change the conclusion for either impact of supplements on length or dosage on length
